\begin{intro}
In the context of mechanical behavior in medicine, there are abundant question to answer, fluctuating from the mathematical modelling itself of different tissues, physiological structures, simulation of its experimental procedures to the verification and prediction of different factor of clinical interest such as density, stiffness constants, etc. From a computational modelling point-of-view, biological tissues define complex multiscale problems since there are multiple physical phenomena acting at various scales. Moreover, from the bast majority of clinical applications the materials are viewed in its continuous setting, thus the importance to contribute with mathematical models and numerical procedures to characterize non-trivial properties arising from the microscopic structures that affect the overall behavior in terms of elasticity or viscosity.
One of particular interest is the human bone, an absorbing complex composite structure that has irregular hollow-like interior filled with marrow, surrounded by soft tissue and muscles. Over it is defined the so-called bone quality, a composite of properties that enables bone to resist fracture. In this sense, when more bone is removed than added in the same time span, the so-called \textit{osteoporosis} condition appear, a established and well-defined disease from the World Health Organization, affecting more than 75 million of people in Europe, United States and Japan combined, being the major cause of fractures.

Nowadays, noninvasive ultrasound techniques corresponds to a unique and important aspect in the biomedical research and applications, as it allows detailed insight of important bone parameters with a lower-cost, non-invasive and non-radiative properties that expects to challenge the gold-standard techniques used in clinical procedures. Under this setting, \textit{Minonzio et. al.} \cite{Minonzio2018} proposed a technique of wave-guide propagation to recover two relevant parameters that describe bone quality, the porosity and thickness of cortical bone using an inverse-like problem formulation. Several questions must be addressed to successfully validate the technique, ranging from the studies of underlying theory used, the effect of domain irregularities and robustness as well as the validation under controlled scenarios.


This work is oriented mainly in the modelling and numerical implementation of such novel ultrasound experimental procedure, in which via homogenization theory techniques it is studied the bone mechanical behavior and  description using the \textit{Lamb}-curves theory. Explicitly, by means of a two-scale asymptotic homogenization framework it is described the macroscopic equations governing the composite material that incorporates the intrinsic non-linear microstructural-driven behavior, defined by the so-called mesoscale.

%It gives us also an explicit step-wise algorithm that first computes the material homogeneous structucture and then describes the macroscopic \footnote{Depending on the literature being used, the macroscopic behavior is also expressed as effective or slow-variable behavior, since is the one that describes the nature defined typically on application fields as evolution problems, i.e. time dependent partial differential equation system.} model underlying the initial setting, allowing us an explicit formulation, thus implementation using the state-of-art \texttt{FEniCS} \cite{logg2012automated} library to compute the solutions of such kind of systems. Thus, providing a methodology to verify and validate using simulated data under controlled settings.

By implementing the ultrasound experimental procedure proposed from \textit{Minonzio, Foiret} \cite{Foiret2014}, \cite{Minonzio2018} with a state-of-art library \texttt{FEniCS} \cite{logg2012automated}, it is simulated  \textit{Lamb}-mode curves and singular values resembling real behavior, assessing the parameter dependency and fidelity. In this context, it is studied properties of the elastic operator to account effects of resonance behavior in the frequency domain and instabilities observed in their spectral decomposition.
Similarly, numerically obtained homogenized elastic coefficients that model the effective mechanical behavior are compared with the reference literate, providing a standpoint towards further modification regarding symmetry and domain configuration.
Finally, from a theoretical stand-point it is studied the justification of the two-scale asymptotic expansion concluding with a convergence result, relating the multiscale solution of the composite material and the homogenized solution. Moreover the extension toward a viscoelasticity formulation is done with damping effects naturally appearing from the complex interaction between several tissues.

This thesis is organized as follows: \textbf{Chapter 1} contextualize the clinical measurements of bone within the novel ultrasound technique and defines the multiscale model used. \textbf{Chapter 2} introduces the two-scale homogenization heuristic providing convergence results and studies of properties derived from the homogenized elastic coefficients. \textbf{Chapter 3} introduces the discretization procedures used for all the numerical implementations. \textbf{Chapter 4} provide results and validation of the numerical simulations done for each case studied. Finally, \textbf{Chapter 5} describes the extension towards a viscoelastic formulation of bone, with justification and numerical results comparable to state-of-art literature.

\end{intro}